On Sample Size for Block Bootstrap Confidence Intervals to Have Desired Coverage Rates

### 2023-04-17 Manuscript/manuscript.tex
Manuscript Update 4/17

\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref, url}
\hypersetup{colorlinks = true, linkcolor = blue, citecolor=blue, urlcolor =
  blue}
\usepackage{natbib}
\usepackage{enumitem}
\usepackage{setspace}

@@

Alternatively, block-bootstrap can be done with overlapping or moving blocks.
Define moving blocks $Z_j = \{X_j, \ldots, X_{j + l - 1}\}$,
$j = 1, \ldots, n - b + 1$. Now we draw $k$ blocks from the $(n - b + 1)$ blocks
of $Z_j$'s with replacement and then aligning them in the order they were picked
to form a block bootstrap sample. If $n$ is not a multiple of~$l$, the last
block selected will be reduced in size so that the final size of the
block bootstrap sample is $n$. Moving block bootstrap was used in
this study as it has been found to yield the lowest error in general
\citep{radovanov2014comparison}. The larger set of available blocks was used.
\jy{what does the last sentence mean?}

@@

\paragraph{Percentile CI}
Let $\hat\theta_{n, B, \alpha}$ be the empirical $100\alpha$th percentile of
$\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$. The $(1 - \alpha)$
empirical percentile CI is
\[
(\hat\theta_{n, \alpha/2}^{(b)}, \hat\theta_{n, 1 - \alpha/2}^{(b)}).
\]
This CI is not necessarily centered by the point estimator $\hat\theta_n$.
%% Not the right place
%% This interval works well when attempting to recover the mean and
%% standard deviation of a temporally dependent process, but its coverage of
%% the temporal dependence deteriorates as $n$ increases.

\paragraph{Centered Percentile CI}
Centered percentile CI is centered at the point estimator and uses the variation
in the bootstrap estimates to construct the error bound. A $(1 - \alpha)$ CI is
\[
(\hat{\theta}_{n} + \delta^*_{\alpha/2},
\hat{\theta}_{n} + \delta^*_{1 - \alpha/2}).
\]
\jy{Define $\delta^*$?}
\jy{Say a few words about its properties}

\paragraph{Bias Corrected and Accelerated (BCA) Bootstrap CI}
The $1 - \alpha$ \% BCA CI takes the form:
\[
(\hat{\theta}_{n} + \delta^*_{\alpha_1},
\hat{\theta}_{n} + \delta^*_{\alpha_2}),
\]
\jy{Not clear and not flowing well. Restructure the writing. Practice my writing tips.}
where $\alpha_{1}$ and $\alpha_{2}$ are the cumulative probability of $z_{1}$ and
$z_{2}$, respectively, where:
\[z_{1} = \frac{z_{0} - z_{1 - \alpha/2}}{1 - a(z_{0} - z_{1 - \alpha/2})} +
z_{0}\] and
\[z_{2} = \frac{z_{0} + z_{1 - \alpha/2}}{1 - a(z_{0} + z_{1 - \alpha/2})} +
z_{0}.\]
Where $z_0$ is the quantile function of the proportion of
$\hat\theta_n^{(b)} < \bar\theta_n^{(b)}$, and $a$ is the skewness (computed
using
the skewness function from the R e1071 package \citep{e1071}) of
$\hat{\theta}_{n, -i}$, where $\hat{\theta}_{n, -i}$ is the statistic of the
original sample computed without the $i^{th}$ block.
\jy{Say a few words about its properties.}

@@

Three target parameters of $X_t$ were considered:
1) $\mu = 0$, the mean of $X_t$;
2) $\sigma_x^2 = 1$, the variance of $X_t$; and
2) $\phi$, the lag-1 auto-correlation coefficient.
To investigate the effect of sample size~$n$, we considered an array of values
$n \in \{100, 200, \ldots, 1000\}$. In each configuration, we generated 1000
replicates. For each replicate, we constructed three 95\% block bootstrap
CIs for each parameter as described in the last section, and
estimated their actual coverage rates along with their 95\% confidence
intervals from the 1000 replicates. The block bootstrap sampling step was done
with function \texttt{tsboot} from R package \textsl{boot} \citep{boot}, with
block size $\lceil n / l \rceil$. This function by default is an implementation
of moving block bootstrap as described in the previous section.
\jy{size? also it was overlapping blocks. Describe the details here.}

@@

\jy{Make it flow better and conciser}
Each interval either recovers $\theta$ or does not. Remember that
95\% of many of a certain type of 95\% CIs constructed from
samples of the same $n$ should recover $\theta$. To see if this is
approximately the case, one can run 1000 replications of the block bootstrap
procedure, and for each interval-$\theta$ pair, the rate at which that type of
interval recovers $\theta$ can be recorded. The coverage rate is, of course, a
point estimate of a proportion, so a 95\% CI of this coverage
proportion (with $n_{CI} = 1000$) can be constructed, and if the proportion
.95 is included in the interval, the block bootstrap method is likely working
well. If all values in the interval are below .95, the results suggest that the
method either is providing an inaccurate estimation, is underestimating the
process' variability, or a combination of both. If all values in the interval
are above .95, the results suggest that the method is overestimating the
process' variability.

@@

- For mu, performance looks about the same regardless of interval type.
- When phi is negative, n = 100 seems large enough.
- When phi is zero, n = 500 is large enough.
- When phi is 0.2, n = 300
- When phi is 0.4, a much larger n seems to be necessary

Based on \ref{fig:mu}, performance is
about the same for the three interval types studied. When $\phi < 0$,
$n = 100$ seems to  be large enough to cover $\mu$ at the nominal rate. When
$\phi = 0$, or in other other words, the sample is from a normal distribution,
$n = 500$ seems to be large enough to cover $\mu$ at the nominal rate. Samples
from processes with $\phi > 0$ appear to require a larger $n$ than samples from
processes with $\phi < 0$. When $\phi = 0.2$, $n = 300$ seemed to be necessary
for adequate performance, and when $\phi = 0.4$, an even larger $n$ appeared
to be necessary to properly cover $\mu$. It is rare for $\phi$ to be so high,
so in most cases, if $\phi$ is unknown, a sample of $n \geq 500$ should be
used when the target parameter is $\mu$.

- For sigma, coverage looks lower for BCa, whereas percentile and centered
look about the same.
- For percentile and centered intervals, n = 400 looks enough when phi = -0.4.
- When phi = -0.2, n = 500 seems to be necessary for percentile and centered
intervals.
- When phi = 0, n = 400 seems to be necessary for percentile and centered
intervals.
- When phi = 0.2, n = 300 seems to be necessary...
- When phi = 0.4, n = 400 seems to be necessary...

Based on \ref{fig:sigma}, coverage is
notably lower for $BC_a$ intervals, but $\hat{\theta}_{n}$-centered intervals
and basic intervals have similar performance. For these two interval types,
$n = 500$ seems to be necessary to cover $\sigma$ at the nominal rate when
$\phi < 0$. If $\phi = 0$, $n = 400$ seems to large enough to cover $\sigma$ at
the nominal rate. If $\phi = 0.2$, $n = 300$ seems large enough, but if the
process has a greater $\phi$ of $0.4$, $n = 400$ may be necessary. It is more
common for $\phi$ to be $> 0$ in applied analysis, so in most cases, if $\phi$
is unknown, using a sample of $n \geq 400$ should be sufficient for estimation
of $\sigma$.

- BCa and percentile deteriorate in coverage as n increases, except for when
phi = 0.
- BCa coverage is very bad when absolute value of phi is high.
- Percentile coverage is not as bad
- n = 200 seems to be enough for centered interval, regardless of phi.

When block bootstrap is used to estimate $\phi$ using $BC_a$ and percentile
intervals, the assumption that coverage rates asymptotically approach the
nominal rate as $n$ increases appears to be invalid based on \ref{fig:sigma}.
The $BC_a$ interval performs very poorly and deteriorates more noticeable
when the absolute value $\phi$ gets
higher, but even when $\phi = 0$, $\phi$ is still undercovered for $n$ as high
as $700$. Like the $BC_a$ interval, the percentile interval deteriorates in
coverage when $\phi$ is high, although the coverage is not as low.
Interestingly, when $\phi = 0$, the percentile interval appears to actually
over-cover $\phi$. These results suggest that $BC_a$ and basic percentile
block bootstrap intervals should not be used estimate temporal dependence
factors of time series. On the other hand, $\hat{\theta}_{n}$-centered
intervals seem to recover $\phi$ correctly as long as $n >= 200$, and this
appears to be true regardless of $\phi$, although a greater $\phi$ may result
in a decline in performance.

@@

To summarize, the interval type chosen should be based on the target parameter.
For estimating $\mu$, any of the three interval types can be used, but for
$\sigma$, only $\hat{\theta}_{n}$-centered and basic percentile intervals
should be used, and only $\hat{\theta}_{n}$-centered intervals should be used
for $\phi$. When estimating
$\mu$, $n = 500$ should be large enough in situations where $\phi$ is unknown.
When estimating $\sigma$, $n = 400$ is sufficient is situations where $\phi$ is
unknown. If $\phi$ is known, a lesser $n$ may be adequate. When estimating
$\phi$, $n = 200$ is large enough when using the correct type of interval.

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_mu}
  \caption{Plots of $\mu$ coverage rates for each interval type and $\phi$
    combination. The orange dotted line represents the 95\% nominal coverage
    rate. The error bars represent a 95\% CI for the coverage
    proportion out of 1000 replications for each $n$. Results from $n$
    ranging from 100-700 were recorded.}
  \label{fig:mu}
\end{figure}

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_sigma}
  \caption{Plots of $\sigma$ coverage rates for each interval type and $\phi$
    combination. The orange dotted line represents the 95\% nominal coverage
    rate. The error bars represent a 95\% CI for the coverage
    proportion out of 1000 replications for each $n$. Results from $n$
    ranging from 100-700 were recorded.}
  \label{fig:sigma}
\end{figure}

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_phi}
  \caption{Plots of $\phi$ coverage rates for each interval type and $\phi$
    combination. The orange dotted line represents the 95\% nominal coverage
    rate. The error bars represent a 95\% CI for the coverage
    proportion out of 1000 replications for each $n$. Results from $n$
    ranging from 100-700 were recorded.}
  \label{fig:phi}
\end{figure}

@@

Block bootstrap method is a useful method for estimating parameters of a time
series: from simple parameters like the mean to temporal dependence factors.
The motivation for the study is the idea that block bootstrap procedure will
perfectly estimate a parameter of a time series given an infinitely large
sample. The goal for this study was to find what is a good enough finite
sample length for block bootstrap estimation to recover the parameter of a
time series at an acceptable rate. Again, this relies on the assumption that
there is a size $n$ large enough for the method to work: that is, the method's
performance improves as $n$ increases. Out of the two types of intervals used
in this study, this assumption was found to hold true with respect to
estimating $\phi$ only for $\hat{\theta}_{n}$-centered intervals, whereas both
percentile $BC_a$ intervals exhibited coverage deterioration as $n$
increased. When using $\hat{\theta}_{n}$-centered intervals and $\phi$ is
unknown, the results of this study suggest that an $n$ of around 500 may be
necessary for common practice to estimate a simple parameter like $\mu$, and
an $n$ of around 400 may be necessary to
estimate $\sigma$. If $\phi$ is already known, a lesser $n$ may be adequate to
estimate these parameters. When $\phi$ was negative, a $n$ of around 100 was
sufficient to estimate $\mu$. However, in real world applications, $\phi$ is
more commonly found to be positive, so a larger $n$ is more likely to be
necessary. Lastly, to estimate $\phi$, an $n$ of around 400 may be necessary.
Further investigation may be necessary to see if there are other interval
corrections that fix the coverage deterioration problem for $\phi$.
This study could be used as a guide for applied statistics courses for students
to generally understand how large of a sample size is sufficient for block
bootstrap to be used versus other inference methods.
This information could prove to be useful for researching using block bootstrap
estimation of time series in domains such as econometrics. Future studies
could investigate if there are types of block bootstrap intervals
constructions that would more appropriately recover the parameters of a time
series. One could also investigate the $n$ needed to make inferences about
other forms of serially dependent data such as an MA process.

@@

BBOB

>>>>

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref, url}
\hypersetup{colorlinks = true, linkcolor = blue, citecolor=blue, urlcolor =
  blue}
\usepackage{natbib}
\usepackage{enumitem}
\usepackage{setspace}

@@

Alternatively, block-bootstrap can be done with overlapping or moving blocks.
Define moving blocks $Z_j = \{X_j, \ldots, X_{j + l - 1}\}$,
$j = 1, \ldots, n - l + 1$. Now we draw $k$ blocks from the $(n - l + 1)$
blocks
of $Z_j$'s with replacement and then aligning them in the order they were
picked
to form a block bootstrap sample. If $n$ is not a multiple of~$l$, the last
block selected will be reduced in size so that the final size of the
block bootstrap sample is $n$. It is also possible to implement moving block
bootstrap while allowing blocks to wrap around the end of the series. In other
words, define moving blocks (assuming $l > 1$):

\begin{equation}
Z_j =
    \begin{cases}
        \{X_j, \ldots, X_{j + l - 1}\} & \text{if } j = 1, \dots, n - l + 1\\
        \{X_j, \ldots, X_n, X_1, \ldots, X_{l - 1}\} & \text{if } j = n - l + 2 ,\dots, n
    \end{cases}
\end{equation}

The second implementation of moving block bootstrap was used in
this study, and moving block bootstrap in general had been found to yield the 
lowest error.
\citep{radovanov2014comparison}.  
\jy{what does the last sentence mean?} Addressed

@@

\paragraph{Percentile CI}
Let $\hat\theta_{n, \alpha}^{(b)}$ be the empirical $100\alpha$th percentile of
$\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$. The $(1 - \alpha)$
empirical percentile CI is
\[
(\hat\theta_{n, \alpha/2}^{(b)}, \hat\theta_{n, 1 - \alpha/2}^{(b)}).
\]
This CI is not necessarily centered by the point estimator $\hat\theta_n$.
%% Not the right place
%% This interval works well when attempting to recover the mean and
%% standard deviation of a temporally dependent process, but its coverage of
%% the temporal dependence deteriorates as $n$ increases.

\paragraph{Centered Percentile CI}
Centered percentile CI is centered at the point estimator and uses the
variation
in the bootstrap estimates to construct the error bound. This interval requires
the computation of $\bar\theta_n^{(b)}$, the mean of all bootstrap point
estimates, and $\delta$, the difference between a point estimate and
$\bar\theta_n^{(b)}$. For $b \in \{1, \ldots, B\}$, we can obtain a
$\delta^{(b)}$ based on the $b$th bootstrap point estimate. Let
$\delta_{\alpha}^{(b)}$ be the empirical $100\alpha$th percentile of
$\{\delta^{(1)}, \ldots,  \delta^{(B)}\}$.  
A $(1 - \alpha)$ centered percentile CI is
\[
(\hat{\theta}_{n} + \delta^{(b)}_{\alpha/2},
\hat{\theta}_{n} + \delta^{(b)}_{1 - \alpha/2}).
\]
This CI is necessarily centered by the point estimator $\hat\theta_n$ and is
asymmetric, as different critical values are used to compute
the lower and upper bounds.
\jy{Define $\delta^*$?} Addressed
\jy{Say a few words about its properties} Addressed

\paragraph{Bias Corrected and Accelerated (BCA) Bootstrap CI}
In this study, the BCA CI is an interval centered at the point estimator.
Let $\hat{G}(c) = \#\{\hat\theta_n^{(b)} < c\}/B$ for $b \in \{1, \ldots, B\}$, let
$z_0 = \Phi^{-1}\{\#\{\hat\theta_n^{(b)} < \hat{\theta}_n\} / B\}$ for $b \in \{1, \ldots, B\}$, let
$\hat{\theta}_{n, -i}$ be the statistic of the sample without the $i^{th}$
block, and let $a$ be $SKEW\{\hat{\theta}_{n, -i}\} / 6$. Then
 $\hat\theta_{BCA}[\alpha] = \hat{G}^{-1}\Phi(z_0 + \frac{z_{0} + z_{\alpha}}{1 - a(z_{0} + z_{\alpha})}).$
A $(1 - \alpha)$ centered percentile CI is
\[
(\hat\theta_{BCA}[\alpha/2],
\hat\theta_{BCA}[1 - \alpha/2]).
\]
This CI is not necessarily centered by the point estimator $\hat\theta_n$.

@@

Three target parameters of $X_t$ were considered:
1) $\mu = 0$, the mean of $X_t$;
2) $\sigma_x^2 = 1$, the variance of $X_t$; and
2) $\phi$, the lag-1 auto-correlation coefficient.
To investigate the effect of sample size~$n$, we considered an array of values
$n \in \{100, 200, \ldots, 1000\}$. In each configuration, we generated 10000
replicates. For each replicate, we constructed three 95\% block bootstrap
CIs for each parameter as described in the last section, and
estimated their actual coverage rates along with their 95\% confidence
intervals from the 10000 replicates. The block bootstrap sampling step was done
with function \texttt{tsboot} from R package \textsl{boot} \citep{boot}, with
block size $\lceil n / l \rceil$. This function by default is an implementation
of moving block bootstrap as described in the previous section.
\jy{size? also it was overlapping blocks. Describe the details here.}

@@

\jy{Make it flow better and conciser}
The coverage rates of the CIs were used to compare the performance of CIs. Let
$\hat\theta_{L, CI}$ and $\hat\theta_{U, CI}$ be the lower bound and upper bound,
respectively, $ for $CI \in \{1, \ldots, n_{CI}\}$, where $n_{CI} is the number of 
CIs.
Then $cov = \#\{$\hat\theta_{L, CI}$ < \theta < $\hat\theta_{U, CI}$ \}/n_{CI}$, $ 
for $CI \in \{1, \ldots, n_{CI}\}$.
The coverage rate is, of course, a
point estimate of a proportion, so a 95\% CI of this coverage
proportion (with $n_{CI} = 10000$) can be constructed. If the proportion
.95 is included in the interval, the block bootstrap method is likely
performing
well. If all values in the interval are below .95, the results suggest that the
method either is providing an inaccurate estimation, is underestimating the
process' variability, or a combination of both. If all values in the interval
are above .95, the results suggest that the method is overestimating the
process' variability.

@@

Based on \ref{fig:mu}, performance is
about the same for the three interval types studied for $\mu$. As dependence gets stronger,
a larger sample size is necessary. For $\mu$, all three types are working asymptotically 
but for finite sizes, they more or less need about the same sample size to have the 
correct coverage. When $\phi < 0$,
$n = 100$ seems to  be large enough to cover $\mu$ at the nominal rate. When
$\phi = 0$, or in other other words, the sample is from a normal distribution,
$n = 500$ seems to be large enough to cover $\mu$ at the nominal rate. Samples
from processes with $\phi > 0$ appear to require a larger $n$ than samples from
processes with $\phi < 0$. When $\phi = 0.2$, $n = 300$ seemed to be necessary
for adequate performance, and when $\phi = 0.4$, an even larger $n$ appeared
to be necessary to properly cover $\mu$. It is rare for $\phi$ to be so high,
so in most cases, if $\phi$ is unknown, a sample of $n \geq 500$ should be
used when the target parameter is $\mu$.

Based on \ref{fig:sigma}, coverage is
notably lower for $BC_a$ intervals, but $\hat{\theta}_{n}$-centered intervals
and basic intervals have similar performance. For these two interval types,
$n = 500$ seems to be necessary to cover $\sigma$ at the nominal rate when
$\phi < 0$. If $\phi = 0$, $n = 400$ seems to large enough to cover $\sigma$ at
the nominal rate. If $\phi = 0.2$, $n = 300$ seems large enough, but if the
process has a greater $\phi$ of $0.4$, $n = 400$ may be necessary. It is more
common for $\phi$ to be $> 0$ in applied analysis, so in most cases, if $\phi$
is unknown, using a sample of $n \geq 400$ should be sufficient for estimation
of $\sigma$. Based on our results, $BC_a$ intervals should not be used to 
estimate $\sigma$.

When block bootstrap is used to estimate $\phi$ using $BC_a$ and percentile
intervals, the assumption that coverage rates asymptotically approach the
nominal rate as $n$ increases appears to be invalid based on \ref{fig:sigma}.
The $BC_a$ interval performs very poorly and deteriorates more noticeable
when the absolute value $\phi$ gets
higher, but even when $\phi = 0$, $\phi$ is still undercovered for $n$ as high
as $700$. Like the $BC_a$ interval, the percentile interval deteriorates in
coverage when $\phi$ is high, although the coverage is not as low.
Interestingly, when $\phi = 0$, the percentile interval appears to actually
over-cover $\phi$. Regardless of whether $\phi$ is positive or negative, these two 
intervals do not perform wellThese results suggest that $BC_a$ and basic percentile
block bootstrap intervals should not be used estimate temporal dependence
factors of time series. On the other hand, $\hat{\theta}_{n}$-centered
intervals seem to recover $\phi$ correctly as long as $n >= 200$, and this
appears to be true regardless of $\phi$, although a greater $\phi$ may result
in a decline in performance.

@@

To summarize, the CI type chosen should be based on the target parameter.
For estimating $\mu$, any of the three interval types can be used, but for
$\sigma$, only $\hat{\theta}_{n}$-centered and basic percentile intervals
should be used, and only $\hat{\theta}_{n}$-centered intervals should be used
for $\phi$. When estimating
$\mu$, $n = 500$ should be large enough in situations where $\phi$ is unknown.
When estimating $\sigma$, $n = 400$ is sufficient is situations where $\phi$ is
unknown. If $\phi$ is known, a lesser $n$ may be adequate. When estimating
$\phi$, $n = 200$ is large enough when using the correct type of interval.

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_mu}
  \caption{Plots of $\mu$ coverage rates for each interval type and $\phi$
    combination. The orange dotted line represents the 95\% nominal coverage
    rate. The error bars represent a 95\% CI for the coverage
    proportion out of 10000 replications for each $n$. Results from $n$
    ranging from 100-700 were recorded.}
  \label{fig:mu}
\end{figure}

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_sigma}
  \caption{Plots of $\sigma$ coverage rates for each interval type and $\phi$
    combination. The orange dotted line represents the 95\% nominal coverage
    rate. The error bars represent a 95\% CI for the coverage
    proportion out of 10000 replications for each $n$. Results from $n$
    ranging from 100-700 were recorded.}
  \label{fig:sigma}
\end{figure}

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_phi}
  \caption{Plots of $\phi$ coverage rates for each interval type and $\phi$
    combination. The orange dotted line represents the 95\% nominal coverage
    rate. The error bars represent a 95\% CI for the coverage
    proportion out of 10000 replications for each $n$. Results from $n$
    ranging from 100-700 were recorded.}
  \label{fig:phi}
\end{figure}

@@

Block bootstrap method is a useful method for estimating parameters of a time
series: from simple parameters like the mean to temporal dependence factors.
The motivation for the study is the idea that block bootstrap procedure will
perfectly estimate a parameter of a time series given an infinitely large
sample. The goal for this study was to find what is a good enough finite
sample length for block bootstrap estimation to recover the parameter of a
time series at an acceptable rate.

Again, this relies on the assumption that
there is a size $n$ large enough for the method to work: that is, the method's
performance improves as $n$ increases. Out of the two types of intervals used
in this study, this assumption was found to hold true with respect to
estimating $\phi$ only for $\hat{\theta}_{n}$-centered intervals, whereas both
percentile $BC_a$ intervals exhibited coverage deterioration as $n$
increased.

When using $\hat{\theta}_{n}$-centered intervals and $\phi$ is
unknown, the results of this study suggest that an $n$ of around 500 may be
necessary for common practice to estimate a simple parameter like $\mu$, and
an $n$ of around 400 may be necessary to
estimate $\sigma$. If $\phi$ is already known, a lesser $n$ may be adequate to
estimate these parameters. When $\phi$ was negative, a $n$ of around 100 was
sufficient to estimate $\mu$. However, in real world applications, $\phi$ is
more commonly found to be positive, so a larger $n$ is more likely to be
necessary. Lastly, to estimate $\phi$, an $n$ of around 400 may be necessary.
Further investigation may be necessary to see if there are other interval
corrections that fix the coverage deterioration problem for $\phi$.

This study could be used as a guide for applied statistics courses for students
to generally understand how large of a sample size is sufficient for block
bootstrap to be used versus other inference methods.
This information could prove to be useful for researching using block bootstrap
estimation of time series in domains such as econometrics. Future studies
could investigate if there are types of block bootstrap intervals
constructions that would more appropriately recover the parameters of a time
series. One could also investigate the $n$ needed to make inferences about
other forms of serially dependent data such as an MA process.

@@

BBOB
B
